\makeheading{Oscar J. Korz, II}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
% table.
%
% ALSO: \rcollength is the width of the right column of the table
% (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{2.25in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
  200 E. Dana Street, Apt. A21 & \textit{Cell:} +1-408-599-1024\\
  Mountain View, CA 94041 & \textit{Email:}
  \href{mailto:okorz001@gmail.com}{okorz001@gmail.com}\\
\end{tabular}


\section{Technical Skills}
\begin{lonelist}
\item[]
\begin{innerlist}
\item User space applications in C, C++, Java, Python and Ruby.

\item Strong understanding of POSIX API (including Berkeley sockets and
    pthreads).

\item Experience with a variety of paradigms included object-oriented,
    procedural, event-driven and functional.

\item Modern development tools including git, Jenkins and CMake.

\item Debian and Ubuntu Linux system administration.
\end{innerlist}
\end{lonelist}


\section{Work History}
\begin{lonelist}

\item[] \textbf{CloudCar, Inc.} \hfill \textbf{May 2013-Current}\\
  \textit{Software Engineer}
  \begin{innerlist}
  \item On a team of 6 engineers, worked on a cross-platform C++ shared
      library. Primarily contributed to embedded Linux and Android NDK ports.
  \item Unified multiple plaform-specific builds into a single build system
      using CMake.
  \item Maintained a Jenkins instance and brought up additional slaves.
  \end{innerlist}

\item[] \textbf{JetHead Development, Inc.} \hfill \textbf{Jun 2011-May 2013}\\
  \textit{Technical Lead} \hfill Jan 2013-May 2013
  \begin{innerlist}
  \item Managed the C31 RVU Client maintenance team. Distributed tasks across a
      team of 3-4 engineers, including myself.

  \item Involved in major architectural decisions for the RVU client software
      stack which is deployed in multiple products. Advised 10-15 engineers
      working on the project.
  \end{innerlist}

\item[]% \textbf{JetHead Development, Inc.} \hfill \textbf{Jun 2011-May 2013}\\
  \textit{Software Engineer} \hfill Jun 2011-Jan 2013
  \begin{innerlist}
  \item Worked on the RVU client software, a C++ project using pthreads
      originally targetting embedded Linux MIPS platforms but since ported to
      other platforms.

  \item On a team of 2-3 engineers, reimplemented the media streaming component
      using an asynchronous event-driven paradigm.

  \item Individually designed and implemented the port to Broadcom's Nexus API.

  \item Individually designed the port to the Sony PlayStation 3. On a team
      of 2-3 engineers, implemented this port while dealing with numerous
      POSIX incompatibility issues as they were discovered.

  \item Transitioned the build from a complicated GNU Makefile framework to
      CMake.
  \end{innerlist}

\item[] \textbf{xOverTime} \hfill \textbf{Oct 2012-Feb 2013}\\
  \textit{System Administrator}
  \begin{innerlist}
  \item Worked part-time independently and remotely on Ubuntu cloud servers.

  \item Installed and maintained Nagios and Ansible. Wrote an Ansible module
      for ufw.
  \end{innerlist}

\item[] \textbf{University of California, Riverside} \hfill \textbf{Mar 2011-Jun 2011}\\
  \textit{Undergraduate Assistant}
  \begin{innerlist}
  \item Evaluated the Puppet and Chef configuration management services.

  \item Maintained a cluster of headless OpenVZ CentOS virtual machines.
  \end{innerlist}

\item[] \textbf{GridIron Systems, Inc.} \hfill \textbf{Jun 2010-Sep 2010}\\
  \textit{Software Engineer}
  \begin{innerlist}
  \item On a team of 2 engineers, maintained and extended a monitoring daemon
      written in Python and using the Twisted library for asynchronous
      processing. Stored records in a postgreSQL database.
  \end{innerlist}

\end{lonelist}
% end Work History


\section{Education}
\textbf{University of California, Riverside} \hfill \textbf{Sep 2006-Jun 2011}\\
  \textit{B.S. Computer Science}
